On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_intro.tex
fig.16..
Jordan curve added
I added an explanation of Jordan curve theorem in Section 3.

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

      \draw[dashed] (0,0)--(1.5,0);
      \draw[dashed] (1.5,0)--(3,0);
      \draw[dashed] (3,0)--(4.5,0);
      \draw[dashed] (4.5,0)--(6,0);
      \draw[->] (0,0)--(60:0.75);
      \draw[->] (1.5,0)--++(60:0.75);
      \draw[->] (3,0)--++(60:0.75);
      \draw[->] (4.5,0)--++(60:0.75);
      \draw (0,0)--(60:1.5);
      \draw (1.5,0)--++(60:1.5);
      \draw (3,0)--++(60:1.5);
      \draw (4.5,0)--++(60:1.5);

      \begin{scope}[shift=(60:1.5)]
        \fill (0,0) circle[radius = 0.1];
        \fill (1.5,0) circle[radius = 0.1];
        \fill (3,0) circle[radius = 0.1];
        \fill (4.5,0) circle[radius = 0.1];
        \draw[dashed] (0,0)--(1.5,0);
        \draw[dashed] (1.5,0)--(3,0);
        \draw[dashed] (3,0)--(4.5,0);
        \draw[->] (0,0)--(-60:0.75);
        \draw[->] (1.5,0)--++(-60:0.75);
        \draw[->] (3,0)--++(-60:0.75);
        \draw[->] (4.5,0)--++(-60:0.75);

        \draw (0,0)--(-60:1.5);
        \draw (1.5,0)--++(-60:1.5);
        \draw (3,0)--++(-60:1.5);
        \draw (4.5,0)--++(-60:1.5);
      \end{scope}

    \end{tikzpicture}
    \caption{zig-zag conformation}
    \label{TTT_zigzag}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[above] at (0:1) {$p_s$};

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[right] at (-60:1) {$p_s$};

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[left] at (-120:1) {$p_s$};

@@

%We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
We say that a neighbor of a point $p$ is reachable from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
It is defined formally as follows:

>>>>

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]

            \draw[white] (60:1) -- (0:0);
            \draw[white] (-60:1) -- (0:0);
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[above] at (0:1) {$p_s$};

@@

          \begin{scope}[xshift=2cm, yshift=2cm]

            \draw[white] (60:1) -- (0:0);
            \draw[white] (-60:1) -- (0:0);
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[right] at (-60:1) {$p_s$};

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw[white] (60:1) -- (0:0);
            \draw[white] (-60:1) -- (0:0);
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[left] at (-120:1) {$p_s$};

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\linewidth]{Fig/jordan_curve.png}
\caption{}
\label{fig:Jordan}
\end{figure}

%We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
We say that a neighbor of a point $p$ is \textit{reachable} from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
For example, in Fig.~\ref{fig:Jordan}, the transcript $w$ is about to step into a tunnel. 
The wall beads $w[i-\ell]$ and $w[i-k]$ are both older than the bead at the entrance, $w[i]$. 
Even if $w[i]$ leaves a free neighbor, the neighbor is not reachable because the the path of a conformation must be non-self-intersecting, and its subpath between these two wall beads divides the plane into two regions, one of which includes the entrance of the tunnel and the other of which includes the exit (Jordan curve theorem \cite{Hales2007}). 
Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
It is defined formally as follows:
